---
title: "Start_analysis_toby"
author: "Toby"
date: "3 January 2019"
output: github_document
---

```{r Nameofchunk1, include=FALSE} 
# This is a way to set default setting for your whole documents
knitr::opts_chunk$set(echo = TRUE)
```

# Add first title

## Comment Section

### Even third layer Comment section
Here we add the comment

- First, The white area is some place that to show after "Knit"
- Second, it can also be use some code eiditng like adding a link: [Yihui's blog](https://yihui.name/en/)


```{r Nameofchunk2, include=TRUE} 
#Inside the chunk, if the include = TRUE, then it shows the text and code and results here

```

```{r, echo = T}
head(cars)
# If echo is TRUE, then the code and results will both show
```


```{r, echo = FALSE}
plot(cars)
# If echo is FALSE, then it just show the results but not the code "plot(cars)"
# For more details, you can go to the setting in each chunk, select output, then you have alot of choice!
```

```{r, include = FALSE}
plot(cars)
# If echo is FALSE, then it just show the results but not the code "plot(cars)"

```

# How do we upload sth on github

1 Save your current file (then you will see new Rmd and md file on your right)
2 Press "commit" and then select the files that your have changed
3 Write a commnt message, then press "Commit"
4 After that, you "Push" your change to Github.
